### 2015-02-14 fundamentals/impl.tex
added prelim citation
split up information-gathering paragraph

The \gls{DRE} consists of three steps: supply-demand information gathering,
resource exchange solution, and trade execution. Importantly, each step is
agnostic with respect to the exchange of resources in question, i.e., the same
procedure is used for both Materials and Products. The information-gathering
step consists of three phases. First, consumers of commodities denote both the
quantity of a commodity they need to consume as well as the target isotopics, or
quality, by posting their demand to the market exchange as a series of
\textit{requests}. An optional collection of demand constraints are associated
with each collection of requests. Collections of requests may be grouped
together, denoting \textit{mutual} requests that represent demand for some
common purpose. For example, a reactor may request UOX and MOX fuel mutually,
indicating that either will satisfy its demand for fuel. Suppliers then respond
to the series of requests with a \textit{bid}. A bid supplies a notion of the
quantity and quality of a resource to match a request. Suppliers may add an
arbitrary number of constraints to accompany bids. For example, an enriched UOX
supplier may supply both a natural Uranium and SWU constraint. Any potential
resource transfer may be denoted as \textit{exclusive}. An exclusive transfer
must either be met fully or not at all in order to support concepts such as the
trading of individual reactor assemblies. Finally, requesting facilities,
institutions and regions may apply \textit{preferences} to each potential
request-bid pairing based on the proposed resource transfer. Therefore, an
institution can apply a higher preference to a partner to which it is congenial;
similarly, a region may negate any transfers of material which have a higher
Uranium enrichment than is allowable.

The \gls{DRE} may be solved either optimally by a mathematical program or
approximately by a simulation-based heuristic \TODO{cite}. If any trade is
denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
then either a heuristic must be used or exchanges must be represented as a
\gls{MILP}. If no exclusive trades exist, a \gls{LP} model may be used. In
practice, LPs solve much faster than \gls{MILP}s. However, the capability to
model both exists in \Cyclus in order to provide users with the desired level of
fidelity.

>>>>

The \gls{DRE} consists of three steps: supply-demand information
gathering, resource exchange solution, and trade execution. Importantly, each
step is agnostic with respect to the exchange of resources in question, i.e.,
the same procedure is used for both Materials and Products.

The information-gathering step begins by polling potential consumers. Agents
denote both the quantity of a commodity they need to consume as well as the
target isotopics, or quality, by posting their demand to the market exchange as
a series of \textit{requests}. An optional collection of demand constraints are
associated with each collection of requests. Collections of requests may be
grouped together, denoting \textit{mutual} requests that represent demand for
some common purpose. For example, a reactor may request UOX and MOX fuel
mutually, indicating that either will satisfy its demand for fuel.

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched UOX supplier may supply both a natural Uranium
and SWU constraint. Any potential resource transfer may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.

Finally, requesting facilities, institutions and regions may apply
\textit{preferences} to each potential request-bid pairing based on the proposed
resource transfer. Therefore, an institution can apply a higher preference to a
partner to which it is congenial; similarly, a region may negate any transfers
of material which have a higher Uranium enrichment than is allowable.

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{Gidden2014}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, LPs solve much faster than
\gls{MILP}s. However, the capability to model both exists in \Cyclus in order to
provide users with the desired level of fidelity.
